---
title: "llama2"
author: "JK4529"
date: "2024-01-18"
output: html_document
---

```{r, include=FALSE}
library(Hmisc)
library(prettyR)
library(rcompanion)
library(dplyr)
library(ggplot2)
library(TukeyC)
library(tidyr)
```

# Statistical Test
```{r}
df <- read.csv('C:/Users/cptas/Downloads/Experiment_replicate_0215_prev_eval_table.csv')
head(df)
```

## total accuracy rate
```{r}
df %>% filter(completeness == 1) %>%
  select(accuracy) %>%
  summarise(n = n(),
            acc = sum(accuracy == 1, na.rm = TRUE),
            acc_ratio = acc/n)
```
Overall acc_ratio is 0.073 (7.3%)  


## total completeness rate
```{r}
df %>% summarise(n = n(),
            complt = sum(completeness == 1, na.rm = TRUE),
            complt_ratio = complt/n)
```
Overall completeness ratio is 0.6635 (66.35%) 


## total compliance rate
```{r}
df %>% summarise(n = n(),
            str = sum(structural_compliance == 1, na.rm = TRUE),
            str_ratio = str/n)
```
Overall structural compliance ratio is 0.0042 (0.42%) 


## Test for top_k and completeness
```{r}
# Create a contingency table
tc_contingency <- table(df$top_n, df$completeness)

tc_contingency
tc_contingency_proportions <- prop.table(tc_contingency, margin = 1)
tc_contingency_proportions
# Perform the chi-squared test
tc_result <- chisq.test(tc_contingency)
print(tc_result)
```
top_10: 77.52%, top_50: 54.83%  


## Test for top_k and structural_compliance
```{r}
# Create a contingency table
ts_contingency <- table(df$top_n, df$structural_compliance)

ts_contingency
ts_contingency_proportions <- prop.table(ts_contingency, margin = 1)
ts_contingency_proportions
# Perform the chi-squared test
ts_result <- chisq.test(ts_contingency)
print(ts_result)
```
Not significant  


## Test for top_k and accuracy
```{r}
df_comp1 <- df %>% filter(completeness == 1)
ta <- df_comp1 %>% select(top_n, accuracy) %>%
  group_by(top_n) %>%
  summarise(n = n(),
            acc = sum(accuracy == 1, na.rm = TRUE),
            acc_ratio = acc/n)
ta
prop.test(ta$acc, ta$n)
```
Not significant  



## Test for input and completeness
```{r}
# Create a contingency table
ic_contingency <- table(df$input_type, df$completeness)

ic_contingency
ic_contingency_proportions <- prop.table(ic_contingency, margin = 1)
ic_contingency_proportions
# Perform the chi-squared test
ic_result <- chisq.test(ic_contingency)
print(ic_result)
```
free_text: 72.23%, hpo_concept: 64.36% (P = 0.004)   

## Test for input and structural_compliance
```{r}
# Create a contingency table
is_contingency <- table(df$input_type, df$structural_compliance)

is_contingency
is_contingency_proportions <- prop.table(is_contingency, margin = 1)
is_contingency_proportions
# Perform the chi-squared test
is_result <- chisq.test(is_contingency)
print(is_result)
```
Not significant

## Test for input and accuracy
```{r}
ia <- df_comp1 %>% select(input_type, accuracy) %>%
  group_by(input_type) %>%
  summarise(n = n(),
            acc = sum(accuracy == 1, na.rm = TRUE),
            acc_ratio = acc/n)
ia
prop.test(ia$acc, ia$n)
```
free_text: 6.19%, hpo_concept: 7.66% (P = 0.4772)  



## Test for gpt_version and completeness
```{r}
# Create a contingency table
gc_contingency <- table(df$gpt_version, df$completeness)

gc_contingency
gc_contingency_proportions <- prop.table(gc_contingency, margin = 1)
gc_contingency_proportions
# Perform the chi-squared test
gc_result <- chisq.test(gc_contingency)
print(gc_result)
```
13b:60.88%, 70b: 77.00%, 7b: 64.93%  

## pairwise(post-hoc)
```{r}
gc_pairwise <- pairwiseNominalIndependence(gc_contingency, fisher = FALSE, gtest  = FALSE, chisq  = TRUE, method = "bonferroni")
print(gc_pairwise)
```
All significant.  

## Test for gpt_version and structural_compliance
```{r}
# Create a contingency table
gs_contingency <- table(df$gpt_version, df$structural_compliance)

gs_contingency
gs_contingency_proportions <- prop.table(gs_contingency, margin = 1)
gs_contingency_proportions
# Perform the chi-squared test
gs_result <- chisq.test(gs_contingency)
print(gs_result)
```


## Test for gpt_version and accuracy
```{r}
ga <- df_comp1 %>% select(gpt_version, accuracy) %>%
  group_by(gpt_version) %>%
  summarise(n = n(),
            acc = sum(accuracy == 1, na.rm = TRUE),
            acc_ratio = acc/n)
ga
prop.test(ga$acc, ga$n)
```
13b:8.72%, 70b: 9.06%, 7b: 5.06%  
  
## pairwise(post-hoc)
```{r}
ga_contingency <- table(df_comp1$gpt_version, df_comp1$acc)
ga_contingency
ga_pairwise <- pairwiseNominalIndependence(ga_contingency, fisher = FALSE, gtest  = FALSE, chisq  = TRUE, method = "bonferroni")
print(ga_pairwise)
```
Not significant.  

  
# Gene analysis
## Odds Ratio
```{r}
# gene number
length(sort(unique(df$true_gene)))

# Odds Ratio
M <- dim(df)[1]
K <- dim(df %>% filter(accuracy == 1))[1]
or <- df %>% group_by(true_gene) %>%
  summarise(m = n(),
            k = sum(accuracy == 1, na.rm = TRUE),
            K = K,
            M = M,
            OR = (k / K) / (m / M)) %>%
  arrange(desc(OR))
  
or

# Supplementary table
tr_or <- or %>%
  select(true_gene, OR)
head(tr_or)
```


## gene appearance
```{r}
zero_accuracy_genes <- or %>% filter(k == 0)
zero_accuracy_genelist <- zero_accuracy_genes$true_gene
zero_accuracy_genenumber <- length(zero_accuracy_genelist)
zero_accuracy_genenumber
zero_accuracy_genelist
```

